\documentclass{book}

\title{Certified Security by Design Applied to the Patrol Based\\
  A Demonstration of CSBD Applicability to Military Operations}
\author{Professor Shiu-Kai Chin, Lori Pickering, Jesse Nathanial Hall, YiHong Guo}
\date{August 2017}

\usepackage{634format}
\usepackage{enumerate}
\usepackage{listings}
\usepackage{textcomp}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{holtex}
\usepackage{holtexbasic}
\usepackage{subfiles}
\usepackage{array}
\usepackage{pdflscape}
\usepackage{textcomp}
\usepackage{multirow}
\usepackage[table]{xcolor}
%\usepackage[usenames, dvipsnames]{color}
\usepackage{graphicx}
\usepackage{color}
\graphicspath{ {diagrams/}{pictures/}{MethodsAP/picture/}{appendix/pictures/}{Intro/picture/} }
\input{commands}

\begin{document}
\lstset{language=ML}
\maketitle{}

\tableofcontents{}

\addcontentsline{toc}{chapter}{List of Figures}
\listoffigures

\addcontentsline{toc}{chapter}{Preface}
\chapter*{Preface}
\label{cha:preface}
\input{./preface/preface}

\addcontentsline{toc}{chapter}{Acknowledgments}
\chapter*{Acknowledgments}
\label{cha:acknowledgments}
  This project involved multiple people at multiple levels. The Principal Investigator was
  Professor Shiu-Kai Chin of Syracuse University’s Department of Engineering and Computer Science.
  Lori Pickering, Graduate Student at Syracuse University’s Department of Engineering and Computer
  Science, primarily worked on the access-control logic (ACL) and higher order logic (HOL)
  implementation of the patrol base. Together with Jesse Nathanial Hall, they constructed the
  idea of translating the patrol base operations into state machines. Jesse, also a student at
  Syracuse University in the iSchool and a [rank] in the U.S. Army, was our subject matter expert.
  Once Jesse and Lori decided on the state machine format, Jesse translated the patrol base operations
  into this format. YiHong Guo came to the project near the end. Nevertheless, he contributed significantly
  to the project. YiHong worked on organizing the documentation in LaTeX.


\chapter{Summary}
\label{cha:summary}


\chapter{Introduction}
\label{cha:introduction}
\input{./Intro/Intro}

\chapter{Methods, Assumptions, and Procedures}
\label{cha:meth-assumpt-proc}
\input{./MethodsAP/map}

\chapter{Results and Discussions}
\label{cha:results-discussions}
\input{./HOLImplementation/HOLImplementation}
%\input{../HOL/ssmPB/HOLReports/HOLPBType.tex}

\chapter{Conclusions}
\label{cha:conclusions}
\input{./conclusion/designConclusions}

\chapter{Recommendations}
\label{cha:recommendations}
\input{./recommendations/designRecommendations}


\chapter{References}
\label{cha:references}
\input{./references/references}


\appendix{}
\renewcommand{\thechapter}{\Alph{chapter}}
\input{./appendix/appendix}

\end{document}