\input{../HOL/ssmPB/HOLReports/HOLPBType.tex}
\input{../HOL/ssmPB/HOLReports/HOLssmPB.tex}

%\input{hi.tex}
\section*{Section Overview}
\label{sec:section-overview}


\section{PBTypeScript.sml}
\label{sec:pbtypescript.sml-1}

\ \\This file contains the datatype definitions used in ssmPB.\ \\
\begin{description}
\item[Datatype Definitions]\ 
  \begin{itemize}
    \item Each state machine implements a set of types that are defined in OMNIType.
    OMNIType defines the datatype \textbf{command} which includes a constructor
    and type for \textbf{SLc slCommand}.
    \textbf{SLc} is the “state level command” constructor and the type is \textbf{slCommand}.
    slCommand is a type that is to be further defined in each state machine.\ \\
    \item Each state machine will implement a definition for \textbf{slCommand}.
    In PBType, this is defined as follows:
    \begin{align*}
    %   slCommand\; =&\;\; crossLD\ \\
    %                  &|\; conductORP\ \\
    %                   &|\; moveToPB\ \\
    %                   &|\; conductPB\ \\
    %                   &|\; completePB\ \\
    %                   &|\; incomplete
      \HOLFreeVar{slCommand} =&\;\; \HOLConst{crossLD}\ \\
      &\HOLTokenBar{} \HOLConst{conductORP}\ \\
      &\HOLTokenBar{} \HOLConst{moveToPB}\ \\
      &\HOLTokenBar{} \HOLConst{conductPB}\ \\
      &\HOLTokenBar{} \HOLConst{completePB}\ \\
      &\HOLTokenBar{} \HOLConst{incomplete}
    \end{align*}
    There are 6 ssmPB commands.
    Except for \textbf{incomplete}, each command corresponds to a transition from one
    state to the next state.\textbf{incomplete} is a command that that does not
    change the state of the machine -- a “not done” command.\ \\
    \item Similarly, OMNIType defines the datatype \textbf{state} which has a “state level state”
      constructor and type \textbf{SLs slState}.  In PBType, \textbf{slState} is defined as follows:
      \begin{align*}
        % slState\; =&\;\; PLAN\_PB\ \\
        %               &|\; MOVE\_TO\_ORP\ \\
        %               &|\; CONDUCT\_ORP\ \\
        %               &|\; MOVE\_TO\_PB\ \\
        %               &|\; CONDUCT\_PB\ \\
        %               &|\; COMPLETE\_PB\ \\
        \HOLFreeVar{slState} =&\;\; \HOLConst{PLAN_PB}\ \\
        &\HOLTokenBar{} \HOLConst{MOVE_TO_ORP}\ \\
        &\HOLTokenBar{} \HOLConst{CONDUCT_ORP}\ \\
        &\HOLTokenBar{} \HOLConst{MOVE_TO_PB}\ \\
        &\HOLTokenBar{} \HOLConst{CONDUCT_PB}\ \\
        &\HOLTokenBar{} \HOLConst{COMPLETE_PB}
      \end{align*}

    \item OMNIType defines the datatype \textbf{output} with the “state level output” constructor
      and type as \textbf{SLo slOutput}.  In PBType, it is implemented as follows:
      \begin{align*}
        % slOutput\; =&\;\; PlanPB\ \\
        %               &|\; MoveToORP\ \\
        %               &|\; ConductORP\ \\
        %               &|\; MoveToPB\ \\
        %               &|\; ConductPB\ \\
        %               &|\; CompletePB\ \\
        %               &|\; unAuthenticated\ \\
        \HOLFreeVar{slOutput} =&\;\; \HOLConst{PlanPB}\ \\
        &\HOLTokenBar{} \HOLConst{MoveToORP}\ \\
        &\HOLTokenBar{} \HOLConst{ConductORP}\ \\
        &\HOLTokenBar{} \HOLConst{MoveToPB}\ \\
        &\HOLTokenBar{} \HOLConst{ConductPB}\ \\
        &\HOLTokenBar{} \HOLConst{CompletePB}\ \\
        &\HOLTokenBar{} \HOLConst{unAuthenticated}
      \end{align*}

    \item OMNITtype defines the datatype \textbf{principal} which has “state role” constructor and
      type \textbf{SR stateRole} as:
      \begin{align*}
        \HOLFreeVar{stateRole} = \HOLConst{PlatoonLeader}
      \end{align*}
  \end{itemize}
\end{description}

\section{ssmPBScript.sml}
\label{sec:ssmpbscript.sml}

\begin{enumerate}
\item \textbf{General Notes}
  \begin{enumerate}
  \item ssmPB is an acronym for “secure state machine patrol base”.  The “Script” notation
    tells HOL that this is to be implemented as a theory.  “.sml” is the standard
    file extension for poly ML type files.\ \\
  \item The importance of ssmPB is two-fold:
    \begin{itemize}
    \item \textit{It implements the top-level state machine in HOL.}
      \item \textit{It serves as a model for the implementation of subsequent state machines in the project.}\ \\
      \end{itemize}
    \item ssmPB uses ssm11 (secure state machine 1.1) as the general secure state machine which it
      parameterizes.  That is, functions and datatypes in ssmPB are used as parameters in the ssm11
      secure state machine.   ssmPB is the first state machine in the project that does this.  Thus,
      it is used as a model for subsequent state machines.  Because of the similarity of all state
      machines in the project, subsequent state machines can be a cut-n-paste adaptation of ssmPB,
      with appropriate updates of datatype names.  Encapsulation of each state machine facilitates
      the use of datatypes with the same name in different state machines.  Concerns about conflicts
      among datatype names while integrating state machines (if time allows) were discussed.  This
      should not pose a problem if time permits for the extension of the project to integration of
      state machines.\ \\
    \item iv.	Because ssmPB is a model for subsequent state machines, the details of ssmPB will
      be described in more detail than for subsequent state machine descriptions.\ \\
    \end{enumerate}
  \item \textbf{Theory File Description}
    \begin{enumerate}
    \item After the appropriate comments and declaration of ssmPB as a structure, HOL must open
      theories which it depends on.
      \begin{itemize}
      \item \textit{open HolKernel Parse boolLib bossLib;}
        \begin{itemize}
          \item \textsl{These are included in ALL HOL theory definitions.}
          \end{itemize}
          \item \textit{open TypeBase listTheory optionTheory;}
        \begin{itemize}
        \item \textsl{These are theories that provide added functionality and theories for
            use in the implementation of HOL theories in general.  They are provided with HOL.}
        \end{itemize}
        \item \textit{open acl_infRules aclDrulesTheory aclrulesTheory;}
        \begin{itemize}
        \item \textsl{These are the access-control logic files implemented by Prof.
            Shiu-Kai Chin and Lockwood Morris.}
        \end{itemize}
        \item \textit{open satListTheory ssm11Theory ssminfRules;}
        \begin{itemize}
        \item \textsl{These are additional theories and rules that are used in the implmentation
            of the state machines.  These were implemented by Prof. Shus-Kai Chin for his
            CIS 634 course at Syracuse University.}
        \end{itemize}
        \item \textit{open OMNITypeTheory PBTypeTheory;}
        \begin{itemize}
        \item \textsl{OMNIType contains datatype definitions that are relevant to ALL state
            machines in the project.  PBTypeTheory contains datatype definitions for ssmPB.}
        \end{itemize}
      \end{itemize}\ \\
    \item PBNS_def , PBOut_def, and secContext_def
      \begin{itemize}
      \item \textsl{These are the \textbf{next state} and \textbf{next output} functions, \textbf{PBNS}
        and PBOut respectively. They describe the behavior of the state machine. Each of these
        functions takes two inputs, the current state followed by a command, and returns the next
        state or the next output, respectively. For example, the transition from the \textbf{PLAN_PB}
        state to the next state \textbf{MOVE_TO_ORP} is given by the ‘state level command” (SLc)
        \textbf{crossLD}. In PBNS_def, this looks like:
        {\large
        \begin{align*}                                    
          \textbf{\HOLConst{PBNS} \HOLConst{PLAN_PB} (\HOLConst{exec} (\HOLConst{SLc} \HOLConst{crossLD})) \HOLSymConst{=} \HOLConst{MOVE_TO_ORP}}
        \end{align*}
     }%
    \item The description is similar for \textbf{PBOut}.   The state level command (SLc)
      \textbf{crossLD} will produce the next output \textbf{MoveToORP}.
      {\large
        \begin{align*}
          \textbf{\HOLConst{PBOut} \HOLConst{PLAN_PB} (\HOLConst{exec} (\HOLConst{SLc} \HOLConst{crossLD})) \HOLSymConst{=} \HOLConst{MoveToORP}}
        \end{align*}
      }%
    \item Each line in these definitions corresponds to a transition in the state machine.
      This list is complete.  That is, all possible transitions are delineated.
    \item Notice that there are three different types of commands (\textbf{exec}, \textbf{trap},
      and \textbf{discard}) that precede each SLc type command.  These are “orders” descripted in
      ssm11.  Because ssmPB is a “secure” state machine, each transition must not only be delineated
      in the appropriate next state and next output functions, the command must be given by an
      authenticated and authorized individual (referred to as a principal in the access-control
      logic).  Further explanation follows.
    \item \underline{Authentication}: Each secure state machine has a list of principals
      (defined in datatype definition \textbf{stateRole} in PBType).  In ssmPB, this list
      contains only one principal named \textbf{PlatoonLeader}.  Thus, \textbf{PlatoonLeader}
      is the only authenticable principal in the ssmPB state machine.  Other state machines
      may contain more than one authenticable principals.  Because only authenticable principals
      can issue commands to the state machine, commands issued by non-authenticable principals
      are “discarded.”  Hence, if a principal other than \textbf{PlatoonLeader} in ssmPB issues
      a command, then that command it discarded.  For example, if the platoon sergeant issues
      the SLc command \textbf{crossLD}  in ssmPB it would be represented in the next state function
      \textbf{PBNS} as:
      {\large
        \begin{align*}
          \textbf{(\HOLConst{PBNS} \HOLConst{PLAN_PB} (\HOLConst{discard} (\HOLConst{SLc} \HOLConst{crossLD})) \HOLSymConst{=} \HOLConst{PLAN_PB})}
        \end{align*}
      }%
      where the ssm11 order \textbf{discard} is used to indicate that this principal is not authenticated
      (or the request is not formatted correctly.  See below.)
    \item \underline{Authorized}: In addition to being authenticated, the principal must be
      authorized to issue any given command.  This is covered in the security context of the
      state machine.   The security context of ssmPB is defined in \textbf{secContext_def}.
      Because there is only one authenticable principal in this state machine, namely
      \textbf{PlatoonLeader}, and this principal is authorized on ALL SLc commands in ssmPB,
      there is only one statement in \textbf{secContext_def}.  \textbf{PlattonLeader} is
      authenticated via the “controls” statement, which indicates that \textbf{PlatoonLeader} “controls”
      any SLc command in ssmPB.
      {\large
        \begin{align*}
          \textbf{\HOLConst{Name} \HOLConst{PlatoonLeader} \HOLConst{controls} \HOLConst{prop} (\HOLConst{SOME} (\HOLConst{SLc} \HOLBoundVar{cmd}))}
        \end{align*}
      }%
      Additional principals could be added to the \textbf{stateRole} datatype definition in
      PBType and these principals could be given authority to execute some or all of the SLc
      commands in this state machine.  These authorizations would be listed in \textbf{secContext_def}.
      Only commands issued by a principal that is both authenticated AND authorized will be executed.
      The \textbf{exec} command precedes commands issued by principals that are authenticated and
      authorized.  For example, a command issued by \textbf{PlatoonLeader} to \textbf{crossLD}
      would be executed causing the state machine to transition from the initial state
      \textbf{PALN_PB} to the next state \textbf{MOVE_TO_ORP}.
      {\large
        \begin{align*}
          \textbf{%PBNS\ PLAN\_PB\ (exec\ (SLc\ crossLD))\;} &=\; \textbf{MOVE\_TO\_ORP}
          (\HOLConst{PBNS} \HOLConst{PLAN_PB} (\HOLConst{exec} (\HOLConst{SLc} \HOLConst{crossLD})) \HOLSymConst{=} \HOLConst{MOVE_TO_ORP})}
        \end{align*}
      }%
    \item \underline{Additional considerations}:  Commands issued by principals that are
      authenticated (i.e., listed in \textbf{stateRole}) but who are not authorized in
      \textbf{secContext_def} for a specific command are “trapped.”  Because there are
      no such additional principals in ssmPB, commands issued in ssmPB will not be trapped.
      They will be either discarded or executed.  Nevertheless, trapped commands are
      delineated in the next state and next output functions for completeness and in the
      event that additional principals are added at a later date.  The \textbf{trap} order
      represents such commands.  An example of a command issued  by an authenticated but
      unauthorized principal to \textbf{crossLD} would be implemented as:
       {\large
        \begin{align*}
          \textbf{%PBNS\ PLAN\_PB\ (trap\ (SLc\ crossLD))\;} &=\; \textbf{PLAN\_PB}
          (\HOLConst{PBNS} \HOLConst{PLAN_PB} (\HOLConst{trap} (\HOLConst{SLc} \HOLConst{crossLD})) \HOLSymConst{=} \HOLConst{PLAN_PB})}
        \end{align*}
      }%
    \item \underline{Other}: Commands that are improperly formatted are also discard in the same
      manner as are commands issued by unauthenticated principals.  \ \\
    }\ \\
  \end{itemize}
\item authenticationTest_def
  \begin{itemize}
  \item \textit{This definition defines which types of requests (i.e., some principal  issues a
      command) are authenticated and by whom, and which are not.  In the access-control logic, a
      principal is declared to HOL by preceding it with the identifier \textbf{Name}.  Thus,
      \textbf{Name PlatoonLeader} provides HOL with the name of the principal who is the subject
      of the statement.  A request is indicated in the access-control logic by the identifier
      \textbf{says}.  In ssmPB, \textbf{PlatoonLeader} is authenticated on commands.  That is,
        \begin{align*}
          \textbf{((Name\ PlatoonLeader)\ says\ (prop\ (cmd:(slCommand\ command)\ order))\;}
        \end{align*}
        Additional authenticable principals would be delineated in the same manner.
        \textbf{authenticationTest_def} fails for all other requests.  This also includes
        improperly formatted statemens.
        \begin{align*}
          \textbf{(authenticationTest\ \_\  =\ F)}
          \end{align*}
      }
    \end{itemize}
  \item ssmPBStateInterp_def
    \begin{itemize}
    \item \textit{This is a state interpretation function.  In ssmPB, it is effectively nil., \textbf{TT}
      is true in the access-control logic.   In subsequent state machines, the state interpretation
      function could be used describe differences in the behavior of the state machine for
      specific states.  For example, if one state required a check-list be completed prior to
      the execution of a transition from one state to the next, then it would be declared in
      this function.\ \\}
    \end{itemize}
    \item secContext_def
      \begin{itemize}
        
    \item \textit{In addition to listing authorities via the \textbf{controls} operator, additional
      security-related definitions would be added here.} \ \\
    \end{itemize}
    \item PlatoonLeader_slCommand_lemma
      \begin{itemize}
    \item \textit{This lemma uses a tactical proof technique (backwards proof) to prove that
      \textbf{PlatoonLeader} is authorized on any SLc command. }\ \\
    \end{itemize}
    \item PlatoonLeader_exec_slCommand_justified_thm
      \begin{itemize}
    \item \textit{This uses the lemma above to prove the biconditional that \textbf{PlattoonLeader}’s
      commands are executed if and only if the command is authenticated and authorized.
      \item WIth this theorem, it is easy to prove the following two theorems.}\ \\
      \end{itemize}
      \item PlatoonLeader_slCommand_verified_thm
        \begin{itemize}
    \item \textit{This theorem proves that if the \textbf{PlatoonLeader}’s command was executed,
      then it must have been verified.   }\ \\
    \end{itemize}
    \item PlatoonLeader_justified_slCommand_exec_thm
      \begin{itemize}
    \item \textit{This theorem proves that if the  \textbf{PlatoonLeader}’s command was authorized,
      then the command is executed.   } \ \\
    \end{itemize}
    \end{enumerate}
  \end{enumerate}

  \begin{center}
  \resizebox{\textwidth}{!}{\begin{tabular}{|m{5em}|c|m{8em}|m{9em}|m{8em}|m{8em}|m{8em}|m{9em}|}
                              \hline
    \multicolumn{8}{|c|}{ }\\
    \multicolumn{8}{|c|}{\textcolor{cyan}{Next State}, Next Output Table}\\
    \multicolumn{8}{|c|}{ }\\
    \hline\hline
    & \cellcolor{cyan}State &&&&&&\\
    \hline
     \rowcolor{lime}Commands/ input &  \cellcolor{white}next state, next output  & crossLD & conductORP & moveToPB & conductPB & completePB & incomeplete \\
     \hline
     & \cellcolor{cyan}PLAN_PB & \textcolor{cyan}{MOVE_TO_ORP}, MoveToORP & \rowcolor{lightgray}  &  &&& \cellcolor{white}\textcolor{cyan}{PLAN_PB}, PlanPB \\
    \hline
     & \cellcolor{cyan}MOVE_TO_ORP & \rowcolor{lightgray}& \cellcolor{white}\textcolor{cyan}{CONDUCT_ORP}, ConductORP & & & & \cellcolor{white}\textcolor{cyan}{MOVE_TO_ORP}, MoveToORP \\
    \hline
     & \cellcolor{cyan}CONDUCT_ORP &\rowcolor{lightgray} & & \cellcolor{white}\textcolor{cyan}{MOVE_TO_PB}, MoveToPB & & & \cellcolor{white}\textcolor{cyan}{CONDUCT_ORP}, ConductORP \\
    \hline
     &\cellcolor{cyan} MOVE_TO_PB & \rowcolor{lightgray}&&& \cellcolor{white}\textcolor{cyan}{CONDUCT_PB}, ConductPB && \cellcolor{white}\textcolor{cyan}{MOVE_TO_PB}, MoveToPB \\
    \hline
     & \cellcolor{cyan}CONDUCT_PB & \rowcolor{lightgray}&&&& \cellcolor{white}\textcolor{cyan}{COMPLETE_PB}, CompletePB & \cellcolor{white}\textcolor{cyan}{CONDUCT_PB}, ConductPB \\
    \hline
     & \cellcolor{cyan}COMPLETE_PB & \rowcolor{lightgray} &&&&& \\
    \hline
  \end{tabular}}
  \end{center}

Next table
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  sublevel conductORP  
  \begin{center}
  \resizebox{\textwidth}{!}{\begin{tabular}{|m{5em}|c|m{5em}|m{8em}|m{8em}|m{8em}|m{9em}|}
                              \hline
    \multicolumn{7}{|c|}{ }\\
    \multicolumn{7}{|c|}{ConductORP \textcolor{cyan}{Next State}, Next Output Table}\\
    \multicolumn{7}{|c|}{ }\\
    \hline\hline
    & \cellcolor{cyan}State &&&&&\\
    \hline
     \rowcolor{lime}Commands/ input &  \cellcolor{white}next state, next output  & secure & actionsIn & withdraw & complete & plIncomplete  \\
     \hline
     & \cellcolor{cyan}CONDUCT_ORP & \textcolor{cyan}{SECURE}, Secure & \rowcolor{lightgray}  &  &&\cellcolor{white}\textcolor{cyan}{CONDUCT_ORP}, ConductORP  \\
    \hline
     & \cellcolor{cyan}SECURE & \rowcolor{lightgray}& \cellcolor{white}\textcolor{cyan}{ACTIONS_IN}, ActionsIn & & & \cellcolor{white}\textcolor{cyan}{SECURE}, Secure  \\
    \hline
     & \cellcolor{cyan}ACTIONS_IN &\rowcolor{lightgray} & & \cellcolor{white}\textcolor{cyan}{WITHDRAW}, Withdraw & & \cellcolor{white}\textcolor{cyan}{ACTIONS_IN}, ActionsIn  \\
    \hline
     &\cellcolor{cyan}WITHDRAW & \rowcolor{lightgray}&&& \cellcolor{white}\textcolor{cyan}{COMPLETE}, Complete & \cellcolor{white}\textcolor{cyan}{WITHDRAW}, Withdraw \\
    \hline

  \end{tabular}}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  sublevel conductPB  
  \begin{center}
  \resizebox{\textwidth}{!}{\begin{tabular}{|m{5em}|c|m{7em}|m{9em}|m{9em}|m{8em}|m{9em}|}
                              \hline
    \multicolumn{7}{|c|}{ }\\
    \multicolumn{7}{|c|}{ConductPB \textcolor{cyan}{Next State}, Next Output Table}\\
    \multicolumn{7}{|c|}{ }\\
    \hline\hline
    & \cellcolor{cyan}State &&&&&\\
    \hline
     \rowcolor{lime}Commands/ input &  \cellcolor{white}next state, next output  & securePB & actionsInPB & withdrawPB & completePB & plIncompletePB  \\
     \hline
     & \cellcolor{cyan}CONDUCT_PB & \textcolor{cyan}{SECURE_PB}, SecurePB & \rowcolor{lightgray}  &  &&\cellcolor{white}\textcolor{cyan}{CONDUCT_PB}, ConductPB  \\
    \hline
     & \cellcolor{cyan}SECURE_PB & \rowcolor{lightgray}& \cellcolor{white}\textcolor{cyan}{ACTIONS_IN_PB}, ActionsInPB & & & \cellcolor{white}\textcolor{cyan}{SECURE_PB}, SecurePB  \\
    \hline
     & \cellcolor{cyan}ACTIONS_IN_PB &\rowcolor{lightgray} & & \cellcolor{white}\textcolor{cyan}{WITHDRAW_PB}, WithdrawPB & & \cellcolor{white}\textcolor{cyan}{ACTIONS_IN_PB}, ActionsInPB  \\
    \hline
     &\cellcolor{cyan}WITHDRAW_PB & \rowcolor{lightgray}&&& \cellcolor{white}\textcolor{cyan}{COMPLETE_PB}, CompletePB & \cellcolor{white}\textcolor{cyan}{WITHDRAW_PB}, WithdrawPB \\
    \hline

  \end{tabular}}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  sublevel MoveToORP  
  \begin{center}
  \resizebox{\textwidth}{!}{\begin{tabular}{|m{5em}|c|m{7em}|m{7em}|m{9em}|m{8em}|m{9em}|}
                              \hline
    \multicolumn{7}{|c|}{ }\\
    \multicolumn{7}{|c|}{MoveToORP \textcolor{cyan}{Next State}, Next Output Table}\\
    \multicolumn{7}{|c|}{ }\\
    \hline\hline
    & \cellcolor{cyan}State &&&&&\\
    \hline
     \rowcolor{lime}Commands/ input &  \cellcolor{white}next state, next output  & pltForm & pltMove & pltSecureHalt & complete & incomplete  \\
     \hline
     & \cellcolor{cyan}PLAN_PB & \textcolor{cyan}{PLT_FORM}, PLTForm & \rowcolor{lightgray}  &  &&\cellcolor{white}\textcolor{cyan}{PLAN_PB}, PLTPlan  \\
    \hline
     & \cellcolor{cyan}PLT_FORM & \rowcolor{lightgray}& \cellcolor{white}\textcolor{cyan}{PLT_MOVE}, PLTMove & & & \cellcolor{white}\textcolor{cyan}{PLT_FORM}, PLTForm  \\
    \hline
     & \cellcolor{cyan}PLT_MOVE &\rowcolor{lightgray} & & \cellcolor{white}\textcolor{cyan}{PLT_SECURE_HALT}, PLTSecureHalt & & \cellcolor{white}\textcolor{cyan}{PLT_MOVE}, PLTMove  \\
    \hline
     &\cellcolor{cyan}PLT_SECURE_HALT & \rowcolor{lightgray}&&& \cellcolor{white}\textcolor{cyan}{COMPLETE}, Complete & \cellcolor{white}\textcolor{cyan}{PLT_SECURE_HALT}, PLTSecureHalt \\
    \hline

  \end{tabular}}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  sublevel MoveToPB 
  \begin{center}
  \resizebox{\textwidth}{!}{\begin{tabular}{|m{5em}|c|m{7em}|m{7em}|m{7em}|m{8em}|m{7em}|}
                              \hline
    \multicolumn{7}{|c|}{ }\\
    \multicolumn{7}{|c|}{MoveToPB \textcolor{cyan}{Next State}, Next Output Table}\\
    \multicolumn{7}{|c|}{ }\\
    \hline\hline
    & \cellcolor{cyan}State &&&&&\\
    \hline
     \rowcolor{lime}Commands/ input &  \cellcolor{white}next state, next output  & pltForm & pltMove & pltHalt & complete & incomplete  \\
     \hline
     & \cellcolor{cyan}PLAN_PB & \textcolor{cyan}{PLT_FORM}, PLTForm & \rowcolor{lightgray}  &  &&\cellcolor{white}\textcolor{cyan}{PLAN_PB}, PLTPlan  \\
    \hline
     & \cellcolor{cyan}PLT_FORM & \rowcolor{lightgray}& \cellcolor{white}\textcolor{cyan}{PLT_MOVE}, PLTMove & & & \cellcolor{white}\textcolor{cyan}{PLT_FORM}, PLTForm  \\
    \hline
     & \cellcolor{cyan}PLT_MOVE &\rowcolor{lightgray} & & \cellcolor{white}\textcolor{cyan}{PLT_HALT}, PLTSecureHalt & & \cellcolor{white}\textcolor{cyan}{PLT_MOVE}, PLTMove  \\
    \hline
     &\cellcolor{cyan}PLT_HALT & \rowcolor{lightgray}&&& \cellcolor{white}\textcolor{cyan}{COMPLETE}, Complete & \cellcolor{white}\textcolor{cyan}{PLT_HALT}, PLTHalt \\
    \hline

  \end{tabular}}
  \end{center}